Privacy Analysis of a Mobile Sensor Application

### 2015-01-15 paper.tex
Further reductions in Section 4

The first important step of improving the public services is by obtaining business intelligence. For the urban mobility scenario the Live+Gov systems provide insight in form of traffic jam detection and usage pattern mining, which allow local authorities to focus their efforts to the most important sites.

@@

	\item \textbf{Security Requirements.}
	Interactions (e.g. threats) that shall not occur within the system in order to achieve its business objectives.

@@

\textbf{T3. Data Theft}
An External infiltrates infrastructure in order to steal personal data and sell it on the black market.
Also the External might be motivated politically and wants to harm the reputation of the System Provider or the Local Authority.
Anyways, this threat would be manifested through a technical attack on either hardware (Packet Capture) or software (buffer overflow, SQL injection).
Such a successful attack could harm the reputation of both System Provider and Local Authority.
The technical competence of System Providers would be proven wrong, therefore they would lose professional reputation.
Local Authorities would lose their political reputation, as it would seem like they had endangered data of Citizens, which lose complete control.
Thus this threat is defined by three conflicts: \textit{Privacy vs. Financial Profit}, \textit{Reputation of Service Provider vs. Political Activism} and \textit{Reputation of Local Authority vs. Political Activism}.
Also this threat describes the classical scenario, where attacks are provoked by \textit{Insecure Infrastructure} (SQL injection) and \textit{Insecure Communication} (Packet Capture).

\textbf{T4. Surveillance}
An External infiltrates infrastructure in order to obtain information
about the citizen and exploit it directly.  In this scenario the
external is supposed to have some direct relationship to the citizen
which motivates his interest to obtain personal information.  Examples
could be a public institution that wants to gain information about
planned activities of the citizens (e.g. Nixon's Watergate scandal or
the recent prosecution of Guardian journalists by GHCQ).  Another
example is an insurance company that seeks to get information about
the citizens life-style in relation to the insured risk, like car
accidents or health hazards.

In this threat the privacy interest of the citizen is in conflict with
the aspirations for power over the citizen by the externals.

@@

\textbf{T2. Excessive Data Mining.}
We assess the likeliness of excessive data mining to be $3$ High, since
these kind of analysis can be performed within the walls of the service
provider, without somebody else noticing, and the service provider himself
has an interest in this activity.

The associated loss, on the other hand can be substantial (Medium
$2$).  For example when GPS data is linked to data from telephone
books the identity of the citizen can be revealed and personal details
like visits to doctors. In the threat scenario, this information is
not leaked to third parties, (which would justify an even higher loss
assessment), but the very existence of this information violates the
citizens privacy.

@@

\subsubsection{Security Requirements}

A set of interactions (e.g. threats) that shall not occur within the system in order to achieve its business objectives. Security requirements are targeted to protect one or more assets.

An example of a security requirement is that a given communication channel shall not be infringed by externals. We included these security requirements into our analysis in Section \ref{subsec:priv-rec}.

>>>>

@@

	\item \textbf{Security Requirements.}
	Interactions (e.g. threats) that shall not occur within the system in order to achieve its business objectives.  We included these security requirements into our analysis in Section \ref{subsec:priv-rec}.

@@

\textbf{T3. Data Theft}
An External infiltrates infrastructure in order to steal personal data and sell it on the black market. Also the External might be motivated politically and wants to harm the reputation of the System Provider or the Local Authority. Such a successful attack could harm the reputation of both System Provider and Local Authority. Thus this threat is defined by three conflicts: \textit{Privacy vs. Financial Profit}, \textit{Reputation of Service Provider vs. Political Activism} and \textit{Reputation of Local Authority vs. Political Activism}.
Also this threat describes the classical scenario, where attacks are provoked by \textit{Insecure Infrastructure} (SQL injection) and \textit{Insecure Communication} (Packet Capture).

\textbf{T4. Surveillance}
An External infiltrates infrastructure in order to obtain information
about the citizen and exploit it directly.  In this scenario the
external is supposed to have some direct relationship to the citizen
which motivates his interest to obtain personal information.  Examples
could be a public institution that wants to gain information about
planned activities of the citizens (e.g. Nixon's Watergate scandal or
the recent prosecution of Guardian journalists by GHCQ). 
In this threat the privacy interest of the citizen is in conflict with
the aspirations for power over the citizen by the externals.

@@

\textbf{T2. Excessive Data Mining.}
We assess the likeliness of excessive data mining to be $3$ High, since
these kind of analysis can be performed within the walls of the service
provider, without somebody else noticing, and the service provider himself
has an interest in this activity. The associated loss, on the other hand can be substantial (Medium $2$).

@@
